Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-10-31 Latex_files/Thesis/main_win.tex
chapter 3 updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\chapter{Appendix}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimation of fluid shear rates via galvano mirror}
An alternative approach to generating fluid shear is to use a 
galvano-mirror to rapidly move a trapped particle in a bulk 
fluid. While typically galvano and gimble mirrors are used to 
trap multiple particles simultaneously, a single micro sphere 
can be moved quickly through a fluid along a preset path. The 
only limitation on the particle's speed being the ratio of the 
trap stiffness to the drag force. For low Reynolds numbers we 
can assume that the fluid flow is inversely proportional to the
distance from the particle surface (see Eq.~\eqref{eq:birefringent_shear})

@@

From figure~\ref{fig:galvano_shear} it is clear that not only is a galvano 
mirror a better option for generating high shear rates but also over a larger 
volume. The only limitation to this method is the effective drag experienced 
by the trapped particle. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\chapter{Appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimation of fluid shear rates via galvano mirror}
An alternative approach to generating fluid shear is to use a 
galvano-mirror to rapidly move a trapped particle in a bulk 
fluid. While typically galvano and gimble mirrors are used to 
trap multiple particles simultaneously, a single micro sphere 
can be moved quickly through a fluid along a preset path. The 
only limitation on the particle's speed being the ratio of the 
trap stiffness to the drag force. For low Reynolds numbers we 
can assume that the fluid flow is inversely proportional to the
distance from the particle surface (see Eq.~\eqref{eq:birefringent_shear})

@@

From figure~\ref{fig:galvano_shear} it is clear that not only is a galvano 
mirror a better option for generating high shear rates but also over a larger 
volume. The only limitation to this method is the effective drag experienced 
by the trapped particle. 
\newpage

\section{Approximation of Area growth rate}
Data collected from \cite{Li1992} provides face growth rates 
for glycine seed crystals in supersaturated solutions. The 
reported growth rates are given in terms of $\mu m/sec$, in 
order to compare to the laser induced nucleation events we 
need some method of converting to area units. In \cite{Li1992}
the seed crystals are viewed from a top down perspective with
the edges marked $L_b$ and $L_c$. The authors calculated the 
face growth rates by:
\begin{align}
	G_{011} = \frac{1}{2}sin(67.5^\circ)\frac{dL_c}{dt} \\
	G_{010} = \frac{1}{2}sin(68.5^\circ)\frac{dL_b}{dt}
\end{align}

The face growth rates are provided in the final paper, its
easy enough to rearrange the two equations to get $dL_c/dt$
and $dL_b/dt$. The area growth rate can be computed via the
chain rule, where we overestimate the area of the glycine 
crystal to have a rectangular cross section of side lengths
$L_b$ and $L_c$. Numerically computing the area gives us an
approximate total growth rate of around $0.02 \mu m^2/min$.
This is also an over estimation of the crystal growth rates 
as in \cite{Li1992} they only consider crystals between 
$30\mu m$ and $80\mu m$ and note that the growth rate of 
smaller crystals is even slower.

Overall this demonstrates clearly that the growth rate of a
single crystal is accelerated by the prescience of an optical
trap, at least just after nucleation. The presence of an 
optical trap close to a larger seed crystal is shown to 
inhibit the growth of the crystal front, both with a stationary
beam \cite{Flannigan2023} and a moving beam (see sec.~
\ref{sec:seed_crystals})
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography
